Pattern matching for\\ $(231,213)$-avoiding permutations

### 2015-02-05 article.tex
modification : used of a variable for the size of the text and motif in the bivinvular section \n modification : typo

			Given a bivincular motif $\bmotif$ avoiding $(231,213)$,
			a text $\ptext$, $i$,$j$ , $i<j$.\\

@@

			if $|\pmotif| \notin  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[|\ptext|]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\

			if $|\pmotif| \notin  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[|\ptext|]<\max$
						}\\
						&\text{$\ptext[|\ptext|]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(|\pmotif|+1,|\ptext|)= true $\\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]+1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]-1)>j$}\\
						&\\

@@

			If $i \notin \x$, $i \in \y$ and i is a descent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext[j]-1):]$
			with the condition that
			$\pmotif[i+1]$ is matched to the element $\ptext[j]-1$.\\

			If $i \notin \x$, $i \in \y$ and i is an ascent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext[j]+1):]$
			with the condition that
			$\pmotif[i+1]$ is matched to the element $\ptext[j]+1$.\\

@@

			There are two cases to consider searching for a match : \\
			If $|\pmotif| \in \x$ there exists a match
			if and only if\\ $\bigcup_{0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\

			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<\min<\max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
			is true.			
			\end{proof}

>>>>

			Given a bivincular motif $\bmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

@@

			if $n_\pmotif \notin  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\

			if $n_\pmotif \notin  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						}\\
						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}[\ptext[j]+1]) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}[\ptext[j]-1]) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
						&\\

@@

			If $i \notin \x$, $i \in \y$ and i is a descent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}[\ptext[j]-1]:]$
			with the condition that
			$\pmotif[i+1]$ is matched to the element $\ptext[j]-1$.\\

			If $i \notin \x$, $i \in \y$ and i is an ascent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}[\ptext[j]+1]:]$
			with the condition that
			$\pmotif[i+1]$ is matched to the element $\ptext[j]+1$.\\

@@

			There are two cases to consider searching for a match : \\
			If $n_\pmotif \in \x$ there exists a match
			if and only if\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\

			If $n_\pmotif \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
			is true.			
			\end{proof}
